### 2016-01-23 AcademicPaperSummaries/PaperSummaries.tex
Added three of the week two networks readings
cc

>>>>

\underline{Keywords:} networks; theory-testing

\underline{Research question and area:} McAdam and Paulsen connect to the literature of mobilization into high-risk political organizations. They primarily connect with the sociology literature, and, for example, don't make reference to free-rider problems that preoccupy the civil wars perspective on this question.
\underline{Summary of argument and mechanism:} McAdam and Paulsen are testing theories about how interpersonal ties and membership in organizations influence identity-based mobilization. The theory holds that social networks reinforce identity-based recruitment appeals by affirming that participation would support salient identity.
\underline{Data \& methods} Social network data generated from 1068 applications for participation in the 1964 Mississippi Freedom Summer project, coded networks based on surveys from participants, rejections, and no-shows and 556 followup surveys. Network-related independent variables operationalized as binary variables coding presence of listed organization or source of support.  Dependent variable was binary for participation in freedom summer; logit (?) statistical model.
\underline{Findings:} Personal ties are most important as sources of influence (vs conduits for information); suggestion that best networks for mobilization is weak ties between lots of tightly linked local organizations. Organizational support more important than individual ties for encouraging participation in a collective action.
\underline{Notes on related papers:} Lots of applicability here to mobilization for violent extremist organizations.

\textbf{Mutz, Diana C. 2002. “The Consequences of Cross-Cutting Networks for Political Participation.” American Journal of Political Science 46(4): 838–55.}

\underline{Keywords:} networks; theory testing

\underline{Research question and research area:} Does homogeneity of political belief in networks influence political participation?
\underline{Summary of argument and mechanism:} Non-homogeneous networks introduce uncertainty by transmitting contradictory information thus making people take longer to decide who to vote for; non-homogenous networks depress willingness to publicly share a position because can not make everyone in the network happy.
\underline{Data \& methods:} Used two 1996 surveys about political participation and political interaction within social networks. Logit model with network information included as binary and count variables.
\underline{Findings:} Results most strongly suggest that cross-cutting networks depress willingness to be demonstrative, rather than that the influence makes people confused about what they want.
\underline{Notes on related papers:} I feel like the conflict-avoidance mechanism here would be a natural fit to update to the 21st century via questionnaires about people's activities on social networking sites. (\textit{e.g.}: in the past x months, have you avoided sharing content that promotes a political or social view because of concern about how people will respond?)

\textbf{McClurg, Scott D. 2003. “Social Networks and Political Participation: The Role of Social Interaction in Explaining Political Participation.” Political Research Quarterly 56(4): 449–64.}

\underline{Research question and research area:} Seems to speak most closely to the social capital literature and social determinants of political participation. 
\underline{Summary of argument and mechanism:} Mechanism is explicitly about information-sharing functions of social networks.
\underline{Data \& methods:} Survey data from 1984 Presidential election gathered in South Bend, Indiana. Unit of analysis is the discussion dyad. Dependent variable is a composite count of political activities beyond voting. Model is negative binomial regression.
\underline{Findings:} 
\underline{Notes on related papers:}
combining this article and the  Mutz findings and adding to the context  of social networks is interesting:
then we have a  clear vector of information (both  passive via FB  events) and active,  via people sharing  their views and  things like articles,  BUT also because some online social networks tend to be maximalist (especially Facebook) they also foster the  development of the type of cross- cutting networks that Mutz finds tends to make people cagy about political activism. I bet that beyond presidential election, social campaigns like support for Black Lives Matter would be a good test case of information sharing through networks (having partisans in online networks might increase access to POV and stories
